%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.3 (30/3/2020)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=1.5cm, footskip=.5cm} % Configure page margins with geometry
% \geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-skyblue} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Cao}{Bittencourt}
\address{Brazilian male, 27 years old, single
\item{1050 Fredolin Wolf Avenue, Pilarzinho, Curitiba, PR 82115-000, BR}
}
\mobile{(+55) 48-99143-4854}

\email{caobittencourt@gmail.com}
\github{CaoBittencourtFerreira}
\linkedin{CaoBittencourtFerreira/en}
% \homepage{www.posquit0.com}
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
%\twitter{@twit}

\position{Research and Development Analyst{\enskip\cdotp\enskip}Data Scientist} % Your expertise/fields
\quote{``Ora et Labora." (St. Benedict)} % A quote or statement

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{Electrolux Recruitment Team}{
Electrolux AB
\\143 S:t Göransgatan, Stadshagen
\\Stockholm, Sweden} % The company being applied to
% \recipient{Company Recruitment Team}{Initech Inc.\\4120 Freidrich Ln.\\Austin, TX 78744} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Job Application for Category Specialist --- Care} % The title of the letter

\letteropening{Dear Recruiter,} % How the letter is opened
% \letteropening{Dear Mr./Ms./Dr. LastName,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

\letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter

\makecvfooter{\today}{Cao Bittencourt Ferreira~~~·~~~Cover Letter}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
  
%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

%------------------------------------------------

\lettersection{About Me}

Hi! My name is Cao and I’m a Data Scientist, Award-Winning Economist, and Psychometrician. I come from Florianópolis, SC, Brazil, but I currently live in Curitiba. I speak both Portuguese and English, and I know a bit of German as well.

I have a Bachelor’s Degree in Economics from EPGE, FGV-RJ (Getulio Vargas Foundation), widely recognized as Latin America's top university. And upon my graduation, I got first place in the Minister Ernane Galvêas Award for Best Undergraduate Thesis, winning a grand prize of R\$10,000.00. Furthermore, the evaluating committee for this competition were unanimous in stating my thesis was not only ``the best", but ``the best, by far" (their own words).

Devoutly Catholic, I very much consider work to be a form of prayer and I strive to live by St. Benedict’s lemma: “Ora et Labora” (Pray and Work). My hobbies include creative writing, reading classical works of Philosophy, Theology and Poetry, working out, and listening to music.
%------------------------------------------------

\lettersection{Why Electrolux?}
Electrolux is a century-old, reliable, yet innovative company. Being part of a business with such a rich history would be very exciting. In addition, the Category Specialist position particularly interests me, as I'm good at and enjoy this type of work. 

\lettersection{Why Me?}
I'm really passionate and knowledgeable about my fields of expertise. And I also have a background in Procurement and Supply Chain Optimization. I like to tackle intellectually stimulating questions, often losing myself in my work and devoting 10+ hours a day to it, as I feel personally motivated to make sense of things. I have a proven track record of solving complex problems using abstract mathematical modelling, Machine Learning, Psychometrics, etc --- and my award-winning thesis is but one example of my high work capacity. Indeed, at my current job as a Data Scientist, I’ve accomplished many remarkable tasks, all of which are detailed on my résumé.
%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}