\cvsection{Authored Programming Packages}
\begin{cvhonors}
\cvhonor{atlas.skew}{``A Skewness Coefficient for Bounded Variables".}{R}{3.0.6}
\cvhonor{atlas.match}{``Quantitative Career Matching".}{R}{3.0.0}
\cvhonor{atlas.letters}{``Letter-Shaped Profiles: A Generalization of 'T-Shaped Skills'".}{R}{2.6.0}
\cvhonor{atlas.eqvl}{``A Multi-Purpose Equivalence Estimator".}{R}{2.2.0}
\cvhonor{atlas.acti}{``ACTI: The Atlas Career Type Indicator".}{R}{2.1.12}
\cvhonor{atlas.efa}{``Automated Exploratory Factor Analysis".}{R}{2.1.2}
\cvhonor{atlas.aeq}{``An Attribute Equivalence Coefficient for Skill Set Analyses".}{R}{2.0.1}
\cvhonor{b3.data}{``Tidy Financial Transactions Data".}{R}{1.3.1}
\cvhonor{atlas.misc}{``Miscellaneous Helper Functions".}{R}{1.2.0}
\cvhonor{atlas.ftools}{``Factor Analysis Tools".}{R}{1.1.1}
\cvhonor{atlas.class}{``A Bounded Variable Classifier".}{R}{1.1.0}
\cvhonor{atlas.kcoef}{``Statistical Analysis of Human Capital".}{R}{1.1.0}
\cvhonor{atlas.comp}{``A Career Profile Competence Coefficient".}{R}{1.0.5}
\cvhonor{atlas.gene}{``A Career Profile Generality Coefficient".}{R}{1.0.5}
\cvhonor{atlas.plot}{``Automated Plotting in R".}{R}{1.0.3}
\cvhonor{atlas.employ}{``An Employability Coefficient".}{R}{1.0.0}
\cvhonor{atlas.fstatics}{``Factor-Analytic Comparative Statics".}{R}{1.0.0}
\cvhonor{atlas.intc}{``A Career Interchangeability Coefficient".}{R}{1.0.0}
\cvhonor{atlas.notiq}{``Accurate IQ Approximations".}{R}{1.0.0}
\cvhonor{atlas.text}{``Dynamic Text Generation".}{R}{1.0.0}
\cvhonor{b3.stats}{``Tidy Financial Transactions Statistics".}{R}{0.11.1}
\cvhonor{nbs.data}{``Standardized Financial Statements of Publicly Traded Companies".}{R}{0.2.1}
\cvhonor{atlas.evol}{``An Evolutionary Model of Occupations".}{R}{0.1.0}
\end{cvhonors}