%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
% ATLAS
\cventry
{Statistician} % Job title
{Atlas Career Guide} % Organization
{Deerfield Beach, FL, USA (remote job)} % Location
{Apr. 2022 -- Current} % Date(s)
{%Description(s) of tasks/responsibilities
\begin{cvitems}
\item {I wrote 17 R packages to standardize my code and facilitate collaboration with the team and deployment in the cloud.}
\item {I automated: \begin{itemize}[leftmargin = 0.25cm] \item{Data visualization with ggplot2.} \item{Exploratory Factor Analysis (EFA).} \item{Dynamic text generation.} \end{itemize}}
\item {I developed and invented the following products: \begin{itemize}[leftmargin = 0.25cm] \item{Career Finder: a psychometric questionnaire that makes precise career recommendations and generates dynamic reports}. \item{Career Roadmap: a statistical procedure for optimizing all stages of one's professional journey, from career choice to skill training, while taking into account expected compensation and users' priorities.} \item{AI Impact Analysis: a tool that estimates the impact of the advent of Artificial Intelligence on users' professional profiles, on 941 occupations registered by the Bureau of Labor Statistics (BLS), and on the entire US labor market.} \item{ACTI: the Atlas Career Type Indicator is my own version of the MBTI (a Jungian typology model) and reveals the user's ``career type", which is composed of a combination of up to 14 factors, that I derived from factor analyzing a huge BLS database. In addition, I created a mechanism to visualize ``professional types" as chemical molecules.} \item{Cognitive Assessment: this cognitive assessment is based on a psychometric method I invented to estimate a user's Intelligence Quotient (IQ) through their professional profile. The results are very close to actual IQ scores, which is relevant in Human Resources and Management, since IQ tests have been banned in American businesses. I've nicknamed my product ``NOT IQ", because it provides reliable IQ estimates, even though \emph{technically} it's not an IQ test.} \end{itemize}}
\item {I invented the following statistical coefficients and procedures: \begin{itemize}[leftmargin = 0.25cm] \item{The skewness coefficient for truncated variables.} \item{The equivalence coefficient}. \item{Various human capital flexibility coefficients: macro and microflexibility (intrafactor, interfactor and aggregate).} \item{A series of career similarity coefficients.} \item{The career interchangeability coefficient.} \item{The coefficient of professional attribute indispensability.} \item{The professional profile generality coefficient.} \item{The professional competence coefficient.} \item{The marginal and aggregate employability coefficients.} \item{The marginal and aggregate competitiveness coefficients.} \item{The marginal cost of human capital coefficient.} \item{The marginal and aggregate time investment coefficients.} \item{A factor-analytic comparative statics method.} \item{And a general performance coefficient for Factor Analysis models.} \end{itemize}}
\end{cvitems}
}

% ESTÁGIO
\cventry
{Data Analyst Intern} % Job title
{Cadarn Consulting} % Organization
{Rio de Janeiro, RJ, BR} % Location
{Jul. 2019 -- Jan. 2020} % Date(s)
{%Description(s) of tasks/responsibilities
\begin{cvitems}
\item {I analyzed large budgetary databases from Mosaic Fertilizers, identifying their most costly and most profitable internal handling operations.}
\item {I proposed alternative economic indices for contract readjustments, providing multi-million dollar cost reductions.}
\item {I prepared hundreds of charts, in an automated manner, to visualize the cost and profitability of Mosaic Fertilizer's internal handling operations.}
\item {I also produced regional and national maps to locate these same operations, as well as current and potential suppliers of internal handling services.}
\end{cvitems}
}

%------------------------------------------------    
\end{cventries}