%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Programming Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvskills}

%------------------------------------------------
\cvskill{R}{Estimation of 4 household equivalence scales based on Brazilian Household Budget Surveys POFs 2002 -- 2003 and 2008 -- 2009.}
\cvskill{R}{Estimation of child costs in Brazil based on Brazilian Household Budget Surveys POFs 2002 -- 2003 and 2008 -- 2009.}
\cvskill{R}{Estimation of median cost of living for multiple family compositions and per capita income levels in Brazil based on Brazilian Household Budget Surveys POFs 2002 -- 2003 and 2008 -- 2009.}
\cvskill{R}{Fundamentalist valuation of companies by sector of activity.}
\cvskill{R}{Options pricing via Black‑Scholes and Binomial models.}
\cvskill{Stata}{Quantitative analyses in Marketing by computing Tobit, Probit, Lingering and Current Effects models.}
\cvskill{Python}{Descriptive statistics for Brazilian Household Budget Surveys POFs 2002 -- 2003 and 2008 -- 2009.}
\cvskill{R}{Estimation of VAR models for 91 countries over the period of 1960 to 2019 in order to assess Granger causality between Gross Domestic Savings and growth of Gross Domestic Product per capita.}
\cvskill{R}{Quantitative analyses in Political Science with electoral data from Rio de Janeiro's 2018 municipal elections.}
\cvskill{Python}{Expediture analyses with my personal financial data.}
\end{cvskills}