%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Skills}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvskills}
\cvskill {Programming}{Python, R, Stata, \LaTeX, MATLAB, VBA.}
\cvskill {DBMS}{MySQL, MariaDB.}
\cvskill {Cloud}{AWS EC2, AWS Lambda, AWS RDS, AWS S3, GitHub.}
\cvskill {BI Tools}{Power BI (basic), R Shiny.}
\cvskill {Web Development}{Markdown, HTML (basic), Bubble (basic).}
\cvskill {Machine Learning}{Supervised and Unsupervised ML algorithms and procedures such as KNN, PCA, SVD, Quadratic Optimization, Linear Programming, Random Forest, K-Means, and Hierarchical Clustering. Also, various regression models, including: OLS, NLS, 2SLS, SUR, BLR, NNLS, BVLS, Beta, Tobit, Probit, and Logistic regressions, Quantile regression, LOESS, GAM, Kernel Smoothing, and so on.}
\cvskill {Econometrics}{Many statistical models, including AR, MA, ARMA, VAR, Lingering and Current Effects models, as well as assessing Granger Causality in time series data.}
\cvskill {Finance}{Enterprise valuation, portfolio management, options pricing, cost of living estimation, analysis and construction of household budgets, estimation of household equivalence scales.}
\cvskill {Psychometrics}{Exploratory Factor Analysis (EFA), evaluation of factors' internal consistency (via Lambda 6, Omega Total, Omega Hierarchical, Lambda 2, Cronbach's Alpha, etc); and a wide range of psychometric testing tools (e.g. Big Five, EPI, MBTI, DISC, Holland Code).}
\cvskill {Languages}{Portuguese, English, German (elementary).}
\cvskill {Office}{Word, Excel, PowerPoint, Jira, Trello.}
\cvskill {Organization}{Scrum, Kanban, XP, Intertemporal Eisenhower matrix, Pomodoro technique.}
\end{cvskills}